Automated Metadata Generation for Fish Specimen Image Collections

### 2021-03-28 paper/paper.tex
Updates from Overleaf
Added more Fish Image refs
Cropped teaser pix

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \centering
  \includegraphics[width=.49\textwidth]{images/teaser1}
  \includegraphics[width=.49\textwidth]{images/teaser2}
  \caption{Initial object detection on specimen images using Detectron2~\cite{wu2019detectron2}}
  \Description{Fish predictions}
  \label{fig:fish}
\end{teaserfigure}

@@

Since the digital collections may each contain tens of thousands of images, producing metadata for each image via a manual process is prohibitively labor-intensive and infeasible. Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.
As a step towards improving metadata in specimen research image collections, members of the Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
extract a set of data features that provide important metadata about the
digital specimen.
The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which aims to develop a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
Using a combination of machine learning and image informatics tools and techniques, we can accurately determine general image quality and metadata such as fish quantity and location within images, fish orientation, and
image scaling based on ruler identification and measurement. Image scaling
allows us to compute quantitative features about the fish specimens, such
as their length and area.  In order to test and validate our methods, they
were  applied to a set of 7,247
images drawn from the Illinois Natural History Survey (INHS) Collection.
The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods. Next, the results are presented, followed by a discussion. The conclusion highlights key findings and identifies next steps.

@@

Bock 2018 \cite{BockAlexander2018TITE},
Konovalov 2017 \cite{KonovalovD2017RDfA},
Williams 2020 \cite{Williams:2020:UIF},
Hao 2015 \cite{Hao2015TheMO},
Lalabadi 2020 \cite{Lalabadi2020FishFC},
Wang 2015 \cite{Huihui2015StudyOT},
Saberioon 2017 \cite{Saberioon2017ApplicationOM},
Tappi 2017 \cite{Tappi2017ComputerVS},
Taheri-Garavand 2019 \cite{TaheriGaravand2019RealtimeNM},
Azarmdel 2019 \cite{Azarmdel2019DevelopingAO},
Bernardo 2020 \cite{Bernardo2020FishQI},
Konovalov 2018 \cite{Konovalov2018AutomaticSO},
Konovalov 2019 \cite{Konovalov2019AutomaticWE},
Lugatiman 2019 \cite{Lugatiman2019TunaMF},
Mu{\~n}oz-Benavent 2018 \cite{MuozBenavent2018EnhancedFB},
Petrov 2020 \cite{Petrov2020Overview},
G{\"u}m{\"u}ş 2011 \cite{Gm2011MachineVA},
Miranda 2017 \cite{MIRANDA201741},
Zion 2000 \cite{Zion2000InvivoFS},
Zion 2012 \cite{Zion2012ReviewTU},
Dowlati 2012 \cite{Dowlati2012ApplicationOM},
Balaban 2010 \cite{Balaban2010UsingIA},
Alsmadi 2010 \cite{Alsmadi2010FishRB},
Isimen 2014 \cite{Iscimen2014ImageAM},
Iqbal 2021 \cite{Iqbal2021AutomaticFS},
Saitoh 2015 \cite{Saitoh2015ImagebasedFR},
Sung 2017 \cite{Sung2017VisionBR},
Sharmin 2019 \cite{Sharmin2019MVB},
Salman 2016 \cite{Salman2016FishSC},
Sung 2020 \cite{Sung2020AutomaticGF},
Xu 2021 \cite{Xu2021TransferLA},
Banan 2020 \cite{Banan2020DeepLA}

>>>>

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \centering
  \includegraphics[width=.45\textwidth]{images/teaser1_crop}
  \hspace{4mm}
  \includegraphics[width=.45\textwidth]{images/teaser2_crop}
  \caption{Initial object detection on specimen images using Detectron2~\cite{wu2019detectron2}}
  \Description{Fish predictions}
  \label{fig:fish}
\end{teaserfigure}

@@

Since the digital collections may each contain tens of thousands of images, producing metadata for each image via a manual process is prohibitively labor-intensive and infeasible. Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.
As a step towards improving metadata in specimen research image collections, members of the Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
extract a set of data features that provide important metadata about the
digital specimen.
The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which aims to develop a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
Using a combination of machine learning and image informatics tools and techniques, we can accurately determine general image quality and metadata, such as fish quantity and location within images, fish orientation, and
image scaling based on ruler identification and measurement. Image scaling
allows us to compute quantitative features about the fish specimens, such
as their length and area.  In order to test and validate our methods, they
were  applied to a set of 7,247
images drawn from the Illinois Natural History Survey (INHS) Collection.
The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods. Next, the results are presented, followed by a discussion. The conclusion highlights key findings and identifies next steps.

@@

Fish Classification\newline
Alsmadi 2010 \cite{Alsmadi2010FishRB},
Alsmadi 2019 \cite{Alsmadi2019RFE},
Hasija 2017 \cite{Hasija2017FishSC},
Hu 2012 \cite{HuJing2012Fscb},
Iqbal 2021 \cite{Iqbal2021AutomaticFS},
Iscimen 2014 \cite{Iscimen2014ImageAM},
Iscimen 2015 \cite{Iscimen2015ClassificationOF},

Orientation, Size and Weight and Shape\newline
Azarmdel 2019 \cite{Azarmdel2019DevelopingAO},
Balaban 2010 \cite{Balaban2010UsingIA},
Wang 2015 \cite{Huihui2015StudyOT},
Hao 2015 \cite{Hao2015TheMO},

Fish Quality\newline
Bernardo 2020 \cite{Bernardo2020FishQI},
Dowlati 2012 \cite{Dowlati2012ApplicationOM},

3D Segmentation from microCT\newline
Bock 2018 \cite{BockAlexander2018TITE},

Computer Vision Overviews to Fish\newline
G{\"u}m{\"u}ş 2011 \cite{Gm2011MachineVA},

Konovalov 2017 \cite{KonovalovD2017RDfA},
Williams 2020 \cite{Williams:2020:UIF},
Lalabadi 2020 \cite{Lalabadi2020FishFC},
Saberioon 2017 \cite{Saberioon2017ApplicationOM},
Tappi 2017 \cite{Tappi2017ComputerVS},
Taheri-Garavand 2019 \cite{TaheriGaravand2019RealtimeNM},
Konovalov 2018 \cite{Konovalov2018AutomaticSO},
Konovalov 2019 \cite{Konovalov2019AutomaticWE},
Lugatiman 2019 \cite{Lugatiman2019TunaMF},
Mu{\~n}oz-Benavent 2018 \cite{MuozBenavent2018EnhancedFB},
Petrov 2020 \cite{Petrov2020Overview},
Miranda 2017 \cite{MIRANDA201741},
Zion 2000 \cite{Zion2000InvivoFS},
Zion 2012 \cite{Zion2012ReviewTU},
Saitoh 2015 \cite{Saitoh2015ImagebasedFR},
Sung 2017 \cite{Sung2017VisionBR},
Sharmin 2019 \cite{Sharmin2019MVB},
Salman 2016 \cite{Salman2016FishSC},
Sung 2020 \cite{Sung2020AutomaticGF},
Xu 2021 \cite{Xu2021TransferLA},
Banan 2020 \cite{Banan2020Deep,LA}
Kinjo 2014 \cite{KinjoAtsushi2014Scoi},
Ogunlana 2015 \cite{Ogunlana2015FCU},
Sayed 2018 \cite{SayedGehadIsmail2018AAFS},
Rodrigues 2015 \cite{RodriguesMarcoT.A2015Ecda},
Shah 2019 \cite{Shah2019FishPakFS},
Li 2014 \cite{Li2014IdentificationOF}
